\documentclass[10pt]{article}

%-------------------------------------------------------------------------
%\usepackage{fullpage}
\usepackage{multicol}
\usepackage{amssymb}
\usepackage[a4paper]{geometry}
\usepackage{color}
\usepackage{multirow}
\usepackage{bm}
\usepackage{array}
\usepackage{amsmath,latexsym} 
\usepackage{csquotes}
\usepackage{verbatim}
\usepackage{ tipa }
\usepackage{enumitem}
%\usepackage[autostyle]{csquotes}

\usepackage[pdftex]{graphicx}
\pagestyle{empty}

\definecolor{bl}{RGB}{170,216,230}  %final
%\definecolor{bl}{RGB}{166,226,230}  %final
\definecolor{mygray}{gray}{0.44}


\newcommand{\hilight}[1]{\colorbox{light-gray}{#1}}
\geometry{left=0.65in, right=0.57in, top=0.70in, bottom=0.5in}

%-------------------------------------------------------------------------
%font san serif family
%\upshape
%\mdseries
\fontfamily{pcr}  % ld
%%\fontfamily{SansSerif}

%-------------------------------------------------------------------------
\setlength{\parindent}{-2mm}
\usepackage{enumitem}
\newlist{myitemize}{itemize}{2}
\setlist[myitemize,1]{label=$\bullet$,leftmargin=8mm,topsep=2mm,itemsep=1.1mm,itemindent=0mm,parsep=-0.5mm}
\setlist[myitemize,2]{label=$-$,leftmargin=9mm,topsep=1mm,itemsep=1mm,itemindent=0mm,parsep=-1mm}
\newcommand\hs{1.3mm}		%horizontal space
%-------------------------------------------------------------------------
\setlength{\tabcolsep}{5pt}
%-------------------------------------------------------------------------

%-------------------------------------------------------------------------
%for horizontal lines
\usepackage[pdftex]{graphicx}
\newcommand{\HRule}{\rule{\linewidth}{0.2mm}}
%-------------------------------------------------------------------------

%-------------------------------------------------------------------------
%spaces in itemize
%\usepackage{enumitem}
%-------------------------------------------------------------------------


\begin{document}

%--------------------------------------------------------------------------

%\vspace*{137pt}    % EARLIER   *********************
\vspace*{115pt}    % 

%-----------------------------------------------------------------------
\colorbox{bl}{\makebox[\textwidth][c]{\centering \bfseries \color{black} MAJOR PROJECT \& SEMINAR}}% \\
\vspace{-0.1cm}
\begin{itemize}[leftmargin=0.4cm]


\item \textbf{An efficient channel estimation scheme in TDD MIMO Systems}\\
Guide: \textit{Prof. Kumar Appaiah, Electrical Engineering, IIT Bombay}\hfill{(\textit{May’19 - Present})}\\\vspace{-0.68cm}
	\begin{itemize}[leftmargin=0.5cm]
    \item Implemented Multi Cell \textbf{MMSE based MIMO }precoding in mulitiple antennas systems which used
non-orthogonal pilots for channel estimation.\vspace{-0.1cm}
    \item Implemented \textbf{covariance} based channel estimation which uses \text{Bayesian} Estimation and analysed its performance based on rate vs antennas.Implemented \textbf{Kalman} filter to estimate channel in \textbf{MIMO} system.\vspace{-0.1cm}
    \item  Design of \textbf{efficient precoding }scheme using channel state information available using \textbf{feedback} and channel
tracking which reduces the effect of \textbf{pilot contamination} on channel estimation.\vspace{-0.1cm}

	\end{itemize}

\vspace{-0.25cm}

\item \textbf{Inter cell interference in Multi Cell MIMO systems 
} \textbf{[M.Tech Seminar]}
\hfill{(\textit{Jul'18 - Nov'18})}\\
Guide: \textit{Prof. Kumar Appaiah, Electrical Engineering, IIT Bombay}\\\vspace{-0.68cm}
	\begin{itemize}
	\item Studied the structure and working of \textbf{MIMO systems} and impact on BER on using Non-orthogonal pilots.\vspace{-0.1cm}
	\item Simulated \textbf{BER vs SNR} for MIMO systems in Interference and Interference free scenarios.\vspace{-0.1cm}

	\end{itemize}\
	\vspace{-0.6cm}	
\end{itemize}

%------------------------------------------------------------
\colorbox{bl}{\makebox[\textwidth][c]{\bfseries \color{black}  WORK EXPERIENCE \& NON ACADEMIC PROJECT}}
\vspace{-0.6cm}
\begin{itemize}[leftmargin=0.4cm]
	\item \textbf{Interview Management Software \textpipe  \hspace{0.05cm} Electrical Engineering Department, IITB} \hfill{(\textit{Feb'18 - present})}\\
\vspace{-0.1cm}
\hspace{-0.09cm}Lead role in building online system that made automatic coordination across interview committees. This system was successfully used in the last \textbf{3} admission sessions.

\end{itemize}
	\vspace{-0.35cm}

\begin{itemize}[leftmargin=0.4cm]
	\item \textbf{Systems Engineer \textpipe  \hspace{0.05cm} Infosys Technology Ltd} \hfill{(\textit{Dec'15 - Jul'17})}\\
		 Work included writing SQL queries to fetch data to the module and to develop features using Oracle ERM tool.
\end{itemize}
\vspace{-0.1cm}
%----------------------------------------------------------------------

\colorbox{bl}{\makebox[\textwidth][c]{\bfseries \color{black} KEY COURSE PROJECTS}}
\vspace{-0.55cm}
\begin{itemize}[leftmargin=0.4cm]

\item \textbf{Scheduling in 4G LTE }
\hfill{(\textit{Jan'18 - Apr'18})}\\
Guide: \textit{Prof. Abhay Karandikar, Electrical Engineering, IIT Bombay}\\\vspace{-0.7cm}

\begin{itemize}
	\item Implemented \textbf{channel aware scheduling} schemes such as \textbf{MT, PF, TTA}. \vspace{-0.1cm}
	\item Compared all schemes based on \textbf{ cell throughput, average user throughput, Jain fairness index}.\vspace{-0.1cm}
\end{itemize}
\vspace{-0.2cm}
	
	
\item \textbf{Simulation of Cellular System in OCTAVE}
\hfill{(\textit{Jan'18 - Apr'18})}\\
Guide: \textit{Prof. Abhay Karandikar, Electrical Engineering, IIT Bombay}\\\vspace{-0.7cm}
	\begin{itemize}
	\item Computed \textbf{SIR}, \textbf{blocking probability} for different cluster sizes and \textbf{sectoring}.\vspace{-0.1cm}
	\item Analyzed \textbf{handover} process and \textbf{ping-pong} rate for different user mobilities and hysteresis values.\vspace{-0.1cm}
	\item Analyzed BER performance for \textbf{space} and \textbf{time diversity} in a slow flat fading Rayleigh channel.\vspace{-0.1cm}
	\item Analyzed BER performance for a single-cell and multi-cell scenario in a \textbf{CDMA} cellular system.
    \end{itemize}
\end{itemize}
	%\vspace{-0.25cm}	

\colorbox{bl}{\makebox[\textwidth][c]{\bfseries \color{black} OTHER COURSE PROJECTS}}
\vspace{-0.55cm}

\begin{itemize}[leftmargin=0.4cm]
\vspace{-0.05cm}
    	
	\item Spam URL classification using Machine Learning
 \textpipe \hspace{0.2cm} \textit{Course: Network Security}\hspace{2.7cm}(\textit{Jan'19 - Apr'19})\vspace{-0.25cm}
 
     \item Image Dehazing using color attenuation prior and dark channel prior \textpipe \hspace{-0.1cm} \textit{Course: Image Processing} \hfill{(\textit{Jul’18 - Nov’18 })}\vspace{-0.25cm}
	
	\item Basic Image Editor tool in Python
  \textpipe \hspace{0.2cm} \textit{Course: Image Processing}\hspace{5.1cm}(\textit{Jul'18 - Nov'18})\vspace{-0.25cm}
	\item Wavelet based leaders and P leaders in Multi Fractal Analysis \textpipe \hspace{0.2cm}  \textit{Course: Wavelets}\hspace{1.95cm}(\textit{Jul'18 - Nov'18})\vspace{-0.25cm}
	
\end{itemize}

\vspace{0.05cm}

%----------------------------------------------------------------------------------
\colorbox{bl}{\makebox[\textwidth][c]{\bfseries \color{black} TECHNICAL SKILLS}}\\
\begin{tabular}{m{1in}m{0.20in}m{4.5in}}
	\\[-3mm]
	\hspace{\hs} \textbf{\textbf{Languages}} &: & {{C, C++, Python, Bash scripting, HTML, PHP}} \\
	\\[-3.5mm]
	\hspace{\hs} \textbf{\textbf{Tools}} &: & {Matlab/Octave, \LaTeX, Git.}\\
	\\[-4mm]
\end{tabular}\\

%-------------------------------------------------------------------------------------------
\colorbox{bl}{\makebox[\textwidth][c]{\bfseries \color{black} POSITIONS OF RESPONSIBILITY}}

\begin{itemize}[leftmargin=0.4cm]
\vspace{-0.2cm}

\item \textbf {Research Assistant:} System Administrator Laboratory, IIT Bombay \hfill{(\textit{Jul'17 - Present})}\\[-0.7cm]
        \begin{itemize}
	\item Building and maintaining website of EE department, maintaining TA feedback and allotment portals\vspace{-0.1cm}
	%\item Provide mail service, storage space, computing facilities and network facilities to department.\vspace{-0.1cm}
	\item Designed online portals and coordinated for the \textbf{automation} of the activities in department admission process
	\end{itemize}
	\vspace{-0.3cm}


\item \textbf{Web Nominee:} Post Graduate Academic Council, IIT Bombay \hfill{(\textit{Jul'18 - Jun'19})}\\[-0.65cm]
\begin{itemize}
\item Designed new web portal for PGAC which is used by all the Post Graduate students of the institute. \vspace{-0.25cm}	

\end{itemize}
			
\item \textbf{Mess Secretary:
 }  Hostel-1, IIT Bombay   \hfill{(\textit{Sep'17 - Mar'18})}\\[-0.65cm]
 \begin{itemize}
\item Managed all mess activities for a mess which catered for 250+ students with an budget of ~8,00,000/- per month. \vspace{-0.25cm}	

\end{itemize}

\vspace{-0.05cm}
\end{itemize}
%\vspace{-0.2cm}
%--------------------------------------------------------------------------------------

\colorbox{bl}{\makebox[\textwidth][c]{\bfseries \vspace{2cm} \color{black} CO \& EXTRA CURRICULAR ACTIVITIES}}
\vspace{-0.58cm}
\begin{itemize}[leftmargin=0.4cm]
    \item { Completed \textbf{Machine Learning} course by \textbf{Andrew Ng} from Coursera. }\hfill{(\textit{2019})}\vspace{-0.2cm}
    	\item {Conducted a introductory session on \textbf{Linux, vim and Git} as a part of Bridge Course. }\hfill{(\textit{2019})}\vspace{-0.2cm}
    \item {Completed a 100 hrs course on \textbf{Chinese} language conducted by International Relations office IIT Bombay.}\hfill{(\textit{2019})}\vspace{-0.2cm}
    \item {Completed Basic course in \textbf{French} Language from Vivekananda Institute of Languages, Hyderabad.}\hfill{(\textit{2013})}\vspace{-0.2cm}
\end{itemize}

%-------------------------------------------------------------------------------------------------



\end{document}
