\documentclass[10pt]{article}

%-------------------------------------------------------------------------
%\usepackage{fullpage}
\usepackage{multicol}
\usepackage{amssymb}
\usepackage[a4paper]{geometry}
\usepackage{color}
\usepackage{multirow}
\usepackage{bm}
\usepackage{array}
\usepackage{amsmath,latexsym} 
\usepackage{csquotes}
\usepackage{verbatim}
\usepackage{ tipa }
\usepackage{enumitem}
%\usepackage[autostyle]{csquotes}

\usepackage[pdftex]{graphicx}
\pagestyle{empty}
%\definecolor{bl}{RGB}{173,216,230} %ankit   123, same %pratik
%\definecolor{bl}{rgb}{0.2, 0.9, 0.9} %light green
%\definecolor{bl}{RGB}{133,220,230} % pratik ********
%\definecolor{bl}{RGB}{173,210,240}  % new


\definecolor{bl}{RGB}{173,216,230}  %final
%\definecolor{bl}{RGB}{166,226,235}  %pratik
\definecolor{mygray}{gray}{0.44}


\newcommand{\hilight}[1]{\colorbox{light-gray}{#1}}
\geometry{left=0.65in, right=0.57in, top=0.70in, bottom=0.5in}

%-------------------------------------------------------------------------
%font san serif family
%\upshape
%\mdseries
\fontfamily{pcr}  % ld
%%\fontfamily{SansSerif}

%-------------------------------------------------------------------------
\setlength{\parindent}{-2mm}
\usepackage{enumitem}
\newlist{myitemize}{itemize}{2}
\setlist[myitemize,1]{label=$\bullet$,leftmargin=8mm,topsep=2mm,itemsep=1.1mm,itemindent=0mm,parsep=-0.5mm}
\setlist[myitemize,2]{label=$-$,leftmargin=9mm,topsep=1mm,itemsep=1mm,itemindent=0mm,parsep=-1mm}
\newcommand\hs{1.3mm}		%horizontal space
%-------------------------------------------------------------------------
\setlength{\tabcolsep}{5pt}
%-------------------------------------------------------------------------

%-------------------------------------------------------------------------
%for horizontal lines
\usepackage[pdftex]{graphicx}
\newcommand{\HRule}{\rule{\linewidth}{0.2mm}}
%-------------------------------------------------------------------------

%-------------------------------------------------------------------------
%spaces in itemize
%\usepackage{enumitem}
%-------------------------------------------------------------------------


\begin{document}

%--------------------------------------------------------------------------

%\vspace*{137pt}    % EARLIER   *********************
\vspace*{114pt}

%--------------------------------------------------------------------------

%-----------------------------------------------------------------------
\colorbox{bl}{\makebox[\textwidth][l]{\bfseries \color{black} MAJOR PROJECT}}% \\
\vspace{-0.08cm}
\begin{itemize}[leftmargin=0.4cm]
\item \textbf{M.Tech Project: An efficient channel estimation scheme in TDD MIMO Systems}
\hfill{(\textit{May'19 - Present})} \\
Guide: \textit{Prof. Kumar Appaiah, Electrical Engineering, IIT Bombay}\\
\vspace{-0.6cm}
\begin{itemize}
\item Implemented \textbf{Multi Cell MMSE based MIMO precoding} in multiple antennas systems which used non-orthogonal pilots for channel estimation.\vspace{-0.1cm}
\item Analysed and implemented \textbf{covariance based channel estimation} which uses Bayesian Estimation in single cell system and observed its performance based on rate vs number of antennas. 
\vspace{-0.1cm}
\end{itemize}
\vspace{-0.2cm}

\begin{itemize}
\item  Working on implemention a basic precoder which utilises the information obtained from \textbf{Kalman} estimate in \textbf{coordinated MIMO} systems.\vspace{-0.1cm}
\end{itemize}

\vspace{-0.2cm}
\begin{comment}
\item\textbf{B.Tech Project: PC Based Wireless Data Acquisition System}
\hfill{(\textit{Jul'13 - Apr'14})} \\
Guide: \textit{Prof. A. M. Shah, Electronics $\&$ Telecommunication Engineering, GCOE Amravati}\\
\vspace{-0.68cm}
\begin{itemize}
	\item \textbf{Designed} a wireless data acquisition system with \textbf{I2C} and \textbf{SPI} protocol implementation. 
	\vspace{-0.1cm}
	\item  Acquisition of data from a set of remote sensors to a system i.e. on-board system and hyperterminal of PC, where the \textbf{analysis} of the acquired data is done continuously and in  \textbf{real-time}.\vspace{-0.1cm}
	\item Used 433 MHz Tx-Rx module for communication between the remote terminal unit and master control unit.
\end{itemize}
\vspace{-0.2cm}

\end{comment}
\end{itemize}
%------------------------------------------------------------
\vspace{0.2cm}
\hspace{-0.25cm}
\colorbox{bl}{\makebox[\textwidth][l]{\bfseries \color{black}  WORK EXPERIENCE \& NON ACADEMIC PROJECT}}

\vspace{-0.1cm}
\begin{itemize}[leftmargin=0.4cm]
	\item \textbf{Interview Management Software \textpipe  \hspace{0.05cm} Electrical Engineering Department, IITB} \hfill{(\textit{Feb'18 - present})}\\
	Guide: \textit{Prof. Bikash kumar Dey, Prof. Madhu N Belur, Electrical Engineering, IIT Bombay}\\
\vspace{-0.65cm}
\begin{itemize}
		\item  \textbf{Lead role }in building online system that made \textbf{automatic
coordination }across interview committees.\vspace{-0.1cm}
		\item The online system allowed committees to decide in \textbf{real-time} using a \textbf{cross platform web application} about interviews.

		\item Built various other \textbf{peripheral
interfaces} to collect data at different times from students and other sources.
		\item This system was used \textbf{successfully} in the last \textbf{3} admission sessions.
	\end{itemize}
\end{itemize}
\vspace{-0.4cm}
\begin{itemize}[leftmargin=0.4cm]
	\item \textbf{Systems Engineer \textpipe  \hspace{0.05cm} Infosys Technology Ltd} \hfill{(\textit{Dec'15 - Jul'17})}\\
	\vspace{-0.65cm}
	\begin{itemize}
\vspace{-0.07cm}
		\item \textbf{Roles and responsibilities:} part of the team which developed an application which automates billing for the customers of the client.\vspace{-0.1cm}
		\item Wrote SQL queries to fetch data to the module and to develop features using Oracle Peoplesoft ERM tool.
	\end{itemize}
\end{itemize}

%----------------------------------------------------------------------

\colorbox{bl}{\makebox[\textwidth][l]{\bfseries \color{black} KEY COURSE PROJECTS AND SEMINAR}}
\vspace{-0.5cm}
\begin{itemize}[leftmargin=0.4cm]


	
\item {Scheduling in \textbf{4G LTE }}\textpipe \hspace{0.2cm} \textit{Course: Wireless Mobile Communication}
\hfill{(\textit{Jan'18 - Apr'18})}\\
\vspace{-0.7cm}
	
	
\item {Simulation of \textbf{Cellular System} in Octave }\textpipe \hspace{0.2cm} \textit{Course: Wireless Mobile Communication}
\hfill{(\textit{Jan'18 - Apr'18})}\\
\vspace{-0.7cm}

\item {Inter cell interference in \textbf{Multi Cell MIMO} systems } \textpipe \hspace{0.2cm} \textit{M.Tech Seminar}
\hfill{(\textit{Jul'18 - Nov'18})}\\
\vspace{-0.7cm}

\item {\textbf{Image Dehazing} using CAP and DCP } \textpipe \hspace{0.2cm} \textit{Course: Image Processing}
\hfill{(\textit{Jul'18 - Nov'18})}\\
\vspace{-0.7cm}

\item {Basic \textbf{Image Editor} tool in \textbf{Python} } \textpipe \hspace{0.2cm} \textit{Course: Image Processing} 
\hfill{(\textit{Jul'18 - Nov'18})}\\
\vspace{-0.7cm}

\item {\textbf{Wavelet based leaders} and \textbf{P-leaders}  }  \textpipe \hspace{0.2cm} \textit{Course: Image Processing}
\hfill{(\textit{Jul'18 - Nov'18})}\\
\vspace{-0.7cm}

\item {\textbf{Spam URL} classification using \textbf{Machine Learning} } \textpipe \hspace{0.2cm} \textit{Course: Network Security}
\hfill{(\textit{Jan'19 - Apr'19})}\\
\vspace{-0.5cm}



\end{itemize}
%-------------------------------------------------------------------------------------------

%----------------------------------------------------------------------------------
\colorbox{bl}{\makebox[\textwidth][l]{\bfseries \color{black} TECHNICAL SKILLS}}\\
\begin{tabular}{m{1in}m{0.20in}m{4.5in}}
	\\[-4mm]
	\hspace{\hs} \hspace{0.12cm}\textbf{\textbf{Languages}} &: & {{C, C++, Python, HTML, PHP, JQuery, Bash scripting.}} \\
	\\[-3.5mm]
	\hspace{\hs} \hspace{0.12cm}\textbf{\textbf{Tools}} &: & {MATLAB, \LaTeX, Git.}\\
	\\[-5mm]
\end{tabular}\\



%-------------------------------------------------------------------------------------------
\colorbox{bl}{\makebox[\textwidth][l]{\bfseries \color{black} POSITIONS OF RESPONSIBILITY}}

\begin{itemize}[leftmargin=0.4cm]
\vspace{-0.2cm}
\item \textbf {System Administrator: Electrical Department, IIT Bombay} 
\hfill{(\textit{Jul'17 - Present})}\\[-0.6cm]
    \begin{itemize}
	\item Building and maintaining the website of EE department, maintaining TA feedback and allotment portals.\vspace{-0.1cm}
	\item Providing mail service, storage space, computing facilities and network facilities to the department.\vspace{-0.1cm}

	\end{itemize}
	\vspace{-0.25cm}
	
	
\item \textbf{Web Nominee: Post Graduate Academic Council, IIT Bombay}
\hfill{(\textit{Jul'18 - Jun'19})}\\[-0.65cm]
    \begin{itemize}
			\item Designed new web portal for PGAC which is used by all the Post Graduate students of the institute. \vspace{-0.1cm}
		
		\end{itemize}
		\vspace{-0.25cm}

\item \textbf{Mess Secretary: Hostel-1, IIT Bombay}
\hfill{(\textit{Sep'17 - Mar'18})}\\[-0.65cm]
    \begin{itemize}
            \item Managed all mess related activities for a mess which catered for 250+ students. \vspace{-0.1cm}

		\end{itemize}
		\vspace{-0.2cm}	
   	
\end{itemize}
\vspace{0.05cm}

%---------------------------------------------------------------------------------
\colorbox{bl}{\makebox[\textwidth][l]{\bfseries \color{black} CO-CURRICULAR ACTIVITIES}}
\vspace{-0.5cm}
\begin{itemize}[leftmargin=0.4cm]
	\item {Completed \textbf{Machine Learning} course by \textbf{Andrew Ng} from Coursera. }\hfill{(\textit{2019})}\vspace{-0.25cm}
	\item {Conducted an introductory session on \textbf{Linux, Vim and Git} as a part of Bridge Course. }\hfill{(\textit{2019})}\vspace{-0.25cm}
	\item {Volunteered for an introductory session on \textbf{Python} which was conducted for more than 100 students.}\hfill{(\textit{2019})}\vspace{-0.25cm}
    \item {Completed a \textbf{100 hrs} course on the \textbf{Chinese} language conducted by IR office, IIT Bombay. }\hfill{(\textit{2019})}\vspace{-0.25cm}
    \item {Completed a short term course on \textbf{Digital System Design} organised by \textbf{C-DAC,} Hyderabad.}\hfill{(\textit{2015})}\vspace{-0.25cm}
	\item {An active member of \textbf{National Service Scheme (NSS)} for 2 years and attended a camp conducted in a village to perform social activities like conducting medical camps, cleaning and painting common facilities like village panchayat, temple etc.} \hfill{(\textit{2013})}\vspace{-0.25cm}
    \item {Completed basic course in the \textbf{French} language from Vivekananda Institute of Languages, Hyderabad.}\hfill{(\textit{2012})}\vspace{-0.25cm}
   	\item {Volunteered for \textbf{$1^{st}$ World Parliament on Spirituality} for a week as part of NSS activity.}\hfill{(\textit{2012})}\vspace{-0.25cm}
	\item {Completed Diploma in spoken English from Vivekananda Institute of Languages, Hyderabad.} \hfill{(\textit{2012})}\vspace{-0.2cm}
   
\end{itemize}

%-------------------------------------------------------------------------------------------------



\end{document}
