\documentclass[10pt]{article}

%-------------------------------------------------------------------------
%\usepackage{fullpage}
\usepackage{multicol}
\usepackage{amssymb}
\usepackage[a4paper]{geometry}
\usepackage{color}
\usepackage{multirow}
\usepackage{bm}
\usepackage{array}
\usepackage{amsmath,latexsym} 
\usepackage{csquotes}
\usepackage{verbatim}
\usepackage{ tipa }
\usepackage{enumitem}
%\usepackage[autostyle]{csquotes}

\usepackage[pdftex]{graphicx}
\pagestyle{empty}
%\definecolor{bl}{RGB}{173,216,230} %ankit   123, same %pratik
%\definecolor{bl}{rgb}{0.2, 0.9, 0.9} %light green
%\definecolor{bl}{RGB}{133,220,230} % pratik ********
%\definecolor{bl}{RGB}{173,210,240}  % new


\definecolor{bl}{RGB}{173,216,230}  %final
%\definecolor{bl}{RGB}{166,226,235}  %pratik
\definecolor{mygray}{gray}{0.44}

%\renewcommand*\familydefault{\sfdefault}
\newcommand{\hilight}[1]{\colorbox{light-gray}{#1}}
\geometry{left=0.65in, right=0.57in, top=0.70in, bottom=0.5in}

%-------------------------------------------------------------------------
%font san serif family
%\upshape
%\mdseries
\fontfamily{pcr}  % ld
%%\fontfamily{SansSerif}

%-------------------------------------------------------------------------
\setlength{\parindent}{-2mm}
\usepackage{enumitem}
\newlist{myitemize}{itemize}{2}
%\setlist[myitemize,1]{label=$\bullet$,leftmargin=8mm,topsep=2mm,itemsep=1.1mm,itemindent=0mm,parsep=-0.5mm}
%\setlist[myitemize,2]{label=$-$,leftmargin=9mm,topsep=1mm,itemsep=1mm,itemindent=0mm,parsep=-1mm}
\setlist[itemize,1]{label=$\bullet$,leftmargin=4mm,topsep=1.5mm,itemsep=1mm,itemindent=0mm,parsep=-0.5mm}
\setlist[itemize,2]{label=$\circ$,leftmargin=4mm,topsep=1mm,itemsep=1mm,itemindent=0mm,parsep=-0.5mm}
\newcommand\hs{1.3mm}		%horizontal space
%-------------------------------------------------------------------------
\setlength{\tabcolsep}{5pt}
%-------------------------------------------------------------------------

%-------------------------------------------------------------------------
%for horizontal lines
\usepackage[pdftex]{graphicx}
\newcommand{\HRule}{\rule{\linewidth}{0.2mm}}
%-------------------------------------------------------------------------

%-------------------------------------------------------------------------
%spaces in itemize
%\usepackage{enumitem}
%-------------------------------------------------------------------------


\begin{document}

%--------------------------------------------------------------------------


\begin{center}
  \begin{tabular}{m{0.5\textwidth}>{\raggedleft}m{0.5\textwidth}>{\raggedright}}
    \textbf{ M ARUN KUMAR} & \textbf{173079004 } \cr 
    \textbf{ Electrical Engineering} & \textbf{M.tech }\cr  
    \textbf{ Indian Institute of Technology Bombay} & \textbf{Male} \cr
    \textbf{ Specialization: Communication Engineering} & \textbf{DOB: 29-04-1994}
  \end{tabular}
\end{center}
%\vspace*{109pt}    % EARLIER   *********************
\begin{centering}
  \begin{tabular*}{1\textwidth}{@{\extracolsep{\fill}}|c|c|c|c|c|}
    \hline
    \textbf{Examination} & \textbf{University} & \textbf{Institute} & \textbf{Year} & \textbf{CPI/ \%} \cr
    \hline
    Post Graduation & IIT Bombay & IIT Bombay & 2020 & 8.58 \cr
    \hline
    Graduation & JNTUH & ATRI & 2015 & 74.08 \cr
    \hline
    Intermediate & Board of Intermediate & Narayana jr Kalashala& 2011 & 90.2 \cr
    \hline
    Matriculation & Board of Secondary Education & Bhashyam High School & 2009 & 90.83\cr
    \hline
  \end{tabular*}
\end{centering}
%--------------------------------------------------------------------------
\begin{comment}
%-----------------------------------------------------------------
\colorbox{bl}{\makebox[\textwidth][l]{\bfseries \color{black} AREAS OF INTEREST}}
\begin{itemize}[itemindent=-4.8mm]
		
	\item[] \hspace{0.01cm}Wireless Communication, Digital Signal Processing, Image Processing.
	
\end{itemize}
%------------------------------------------------------------------------
\end{comment}
%-----------------------------------------------------------------------
\colorbox{bl}{\makebox[\textwidth][l]{\bfseries \color{black} MAJOR PROJECT AND SEMINAR}}% \\

\begin{itemize}[leftmargin=0.4cm]
\item \textbf{M.Tech Project:An Efficient feedback for postcoder information in MIMO TDD systems}
\hfill{(\textit{May'19 - Present})} \\
Guide: \textit{Prof. Kumar Appaiah, Electrical Engineering, IIT Bombay}


\textbf{Completed work:}Parameterized the feedback for postcoder in massive MIMO TDD systems with multi antenna users. 

\begin{itemize}

\item Formulated a \textbf{lower bound} on the achievable rate for systems with perfect CSIT and partial CSIR.

\item Showed that less than \textbf{10 bits} are requried to feedback the CSI for system with \textbf{ 2 antennas} at UE and around\textbf{ 18 bits} for a system with \textbf{3 antennas} at UE.  

\item Derived a generalised expression for \textbf{upper bound} on the expectation of postcoder error. 

\item Implemented Multi Cell MMSE based MIMO precoding in multiple antenna cellular systems which used non-orthogonal pilots for channel estimation.

\end{itemize}


\item \textbf{M.Tech Seminar: Inter cell interference in Multi Cell MIMO systems 
} 
\hfill{(\textit{Jul'18 - Nov'18})}\\
Guide: \textit{Prof. Kumar Appaiah, Electrical Engineering, IIT Bombay}
	\begin{itemize}
	\item Studied the structure and working of \textbf{MIMO systems} and impact on BER upon using Non-orthogonal pilot sequences for channel estimation.
	\item Simulated \textbf{BER vs SNR} for MIMO systems in Interference and Interference-free scenarios to study the impact of pilot contamination on the performance of the system.

	\end{itemize}
	

\end{itemize}
%------------------------------------------------------------
\hspace{-0.25cm}
\colorbox{bl}{\makebox[\textwidth][l]{\bfseries \color{black}  WORK EXPERIENCE}}

\begin{itemize}[leftmargin=0.4cm]
	\item \textbf{Systems Engineer \textpipe  \hspace{0.05cm} Infosys Technology Ltd} \hfill{(\textit{Dec'15 - Jul'17})}
	
	\begin{itemize}
	    \item  \textbf{Tools Used:} Oracle Peoplesoft.
		\item \textbf{Roles and responsibilities:} Part of the team which developed an application which automates billing for the customers of the client.
		\item Wrote code for fetching data into the module and to develop features using Oracle Peoplesoft ERM tool.
		\item Assisted in designing billing template in XML and in completion of Technical Document Report for the project.
	
	\end{itemize}
\end{itemize}

%----------------------------------------------------------------------

\colorbox{bl}{\makebox[\textwidth][l]{\bfseries \color{black} KEY PROJECTS}}

\begin{itemize}[leftmargin=0.4cm]

\item \textbf{Interview Management Software   \hspace{0.05cm} [Non-Academic Project]} 
\hfill{(\textit{Feb'18 - Dec'20})}\\
Guide: \textit{Prof. Bikash Kumar Dey, Prof. Madhu N. Belur, Electrical Engineering, IIT Bombay}

\begin{itemize}

	\item \textbf{Lead role }in building an online system that made \textbf{automatic
coordination }across interview committees possible through their interface.
	\item The online system allowed committees to decide in \textbf{real-time} using a \textbf{cross platform web application} about interviews.
	\item Built various other \textbf{peripheral
interfaces} to collect data at different times from students and other sources.
	\item This system was used \textbf{successfully} in the last \textbf{3} admission sessions.
\end{itemize}


	
\item \textbf{Scheduling in 4G LTE }
\hfill{(\textit{Jan'18 - Apr'18})}\\
Guide: \textit{Prof. Abhay Karandikar, Electrical Engineering, IIT Bombay}

	\begin{itemize}
	\item Studied different scheduling schemes for \textbf{resource block allocation} to users in \textbf{LTE} systems.
	\item Implemented \textbf{channel aware scheduling} schemes such as Maximum Throughput, Proportional Fairness, Throughput to Average and compared all three scheduling schemes based on metrics such as \textbf{cell throughput, average user throughput and Jain Fairness index}.
    \end{itemize}

	
	
%\newpage	
\item \textbf{Simulation of Cellular System in Octave}
\hfill{(\textit{Jan'18 - Apr'18})}\\
Guide: \textit{Prof. Abhay Karandikar, Electrical Engineering, IIT Bombay}
	\begin{itemize}
	\item Computed \textbf{SIR}, \textbf{blocking probability} for different cluster sizes and \textbf{sectoring}.
	\item Analyzed \textbf{handover} process and \textbf{ping-pong} rate for different user mobilities and hysteresis values.
	\item Analyzed BER performance for \textbf{space} and \textbf{time diversity} in a slow flat fading Rayleigh channel.
	\item Analyzed BER performance for a single-cell and multi-cell scenario in a \textbf{CDMA} cellular system.
    \end{itemize}

		
	



\item \textbf{Image Dehazing  } \hfill{(\textit{Jul'18 - Nov'18})}\\
Guide: \textit{Prof. Amit Sethi, Electrical Engineering, IIT Bombay}
	\begin{itemize}
	\item Implemented \textbf{Color Attenuation Prior and Dark Channel Prior} techniques to estimate the depth map.
	\item Implemented \textbf{Guided Filter} to reconstruct the Haze-free image using Hazy Image and its depth map.
	\end{itemize}
	

\item \textbf{Basic Image Editor tool in Python 
} 
\hfill{(\textit{Jul'18 - Nov'18})}\\
Guide: \textit{Prof. Amit Sethi, Electrical Engineering, IIT Bombay}
	\begin{itemize}
	\item Built a \textbf{GUI tool using pyQt} to implement Histogram equalisation, Gamma correction, Log transformation, Horizontal and Vertical edge detection using Sobel operators, blurring and sharpening with a mechanism to control the extent of blurring and sharpening respectively.
	\item Implemented \textbf{Image Deblurring} using Inverse filter, Truncated inverse filter, Weiner filter, Constrained least square filter and analysed the performance with help of metrics PSNR and SSIM.
	\end{itemize}


\item \textbf{Wavelet based leaders and P-leaders in Multi
Fractal Analysis} 
\hfill{(\textit{Jul'18 - Nov'18})}\\
Guide: \textit{Prof. Vikram M Gadre, Electrical Engineering, IIT Bombay}
	\begin{itemize}
	\item Studied about \textbf{p-exponents} and multi-resolution quantity called \textbf{p-leaders} used to measure negative regularity which appear in most real time signal analysis.
	\item Simulated p-leaders for several signals and was able to prove their convergence with \textbf{DWT based Wavelet leaders} as \textbf{p} becomes large.
	\end{itemize}
	

\item \textbf{Spam URL classification using Machine Learning}
\hfill{(\textit{Jan'19 - Apr'19})}\\
Guide: \textit{Prof. Gaurav S kasbekar, Electrical Engineering, IIT Bombay}

	\begin{itemize}
	\item Studied 3 among the Top-10 vulnerabilities of \textbf{OWASP} Standard mainly \textbf{XML external entity} attack, \textbf{SQL injection}, \textbf{cross site scripting} with practical implementation and proposed solutions.
	\item Classification of URLs using Machine Learning Techniques like \textbf{Logistic Regression, Naive Bayes, Support Vector Machine, One-vs-Rest}.
	\item An increase of more than \textbf{2 percent} in accuracy was obtained by replacing logistic regression by One-vs-Rest.
    \end{itemize}

	


\end{itemize}
%-------------------------------------------------------------------------------------------
\hspace{-0.17cm}\colorbox{bl}{\makebox[\textwidth][l]{\bfseries \color{black} RELEVANT COURSES}}% \\
	 	
		\begin{tabular}{m{2.3in}m{2.3in}m{2.5in}}
		\hspace{0.55cm}\textbullet\ DSP and its Applications &  \textbullet\ Wireless Mobile Communications  & \textbullet\ Image processing \\
		\hspace{0.55cm}\textbullet\ Statistical Signal Analysis & \textbullet Applied Liner Algebra & \textbullet\ Network Security \\
	\end{tabular}
	
	
	
	
%----------------------------------------------------------------------------------
\colorbox{bl}{\makebox[\textwidth][l]{\bfseries \color{black} TECHNICAL SKILLS}}\\
\begin{tabular}{m{1in}m{0.20in}m{4.5in}}
	\\[-3mm]
	\hspace{\hs} \hspace{0.12cm}\textbf{\textbf{Languages}} &: & {{C, C++, Python, HTML, PHP, JQuery, Bash scripting.}}\\
	\\[-3.5mm]
	\hspace{\hs} \hspace{0.12cm}\textbf{\textbf{Tools}} &: & {MATLAB, \LaTeX, Git.}\\
	\\[-4mm]
\end{tabular}\\



%-------------------------------------------------------------------------------------------
\colorbox{bl}{\makebox[\textwidth][l]{\bfseries \color{black} POSITIONS OF RESPONSIBILITY}}

\begin{itemize}[leftmargin=0.4cm]

\item \textbf {System Administrator: Electrical Department, IIT Bombay} 
\hfill{(\textit{Jul'17 - Present})}
    \begin{itemize}
	\item Building and maintaining the website of EE department, maintaining TA feedback and allotment portals.
	\item Providing mail service, storage space, computing facilities and network facilities to the department.
	\item Handled the Department M.Tech and PhD Admission process. Helped in generation of admit cards, coordinating the answer sheet corrections.
	\end{itemize}
	
	
\item \textbf{Web Nominee: Post Graduate Academic Council, IIT Bombay}
\hfill{(\textit{Jul'18 - Jun'19})}
    \begin{itemize}
			\item Designed new web portal for PGAC which is used by all the Post Graduate students of the institute. 	
	\end{itemize}
	

\item \textbf{Mess Secretary: Hostel-1, IIT Bombay}
\hfill{(\textit{Sep'17 - Mar'18})}
    \begin{itemize}
            \item Managed all mess related activities for a mess which catered for 250+ students with an approximate budget of 8,00,000/- per month.
            %\item Responsible for verification of mess bills, coordinating with vendors.
			%\item Reduced mess bill from Rs-140/- per student per day to around Rs-110/- per students per day in span of two months.
		\end{itemize}
			


    	
\end{itemize}


%---------------------------------------------------------------------------------
\colorbox{bl}{\makebox[\textwidth][l]{\bfseries \color{black} CO-CURRICULAR ACTIVITIES}}

\begin{itemize}
        \item {Received ceritificate of appreciation form Electrical Engineering Dept. IIT Bombay, for excellent contribution in Ph.D Admissions in the Department}. \hfill{(\textit{2019})}
        \item {Received certificate of appreciation for excellence in Teaching Assistantship for the commendable work done as Research Assistant in System Administration Lab (PC Lab) of Electrical Engineering Dept. IIT Bombay}\hfill{(\textit{2019})}. 
	\item {Completed \textbf{Machine Learning} course by \textbf{Andrew Ng} from Coursera. }\hfill{(\textit{2019})}
	\item {Conducted an introductory session on \textbf{Linux, Vim and Git} as a part of Bridge Course which helps in smooth transition of new joiners to the institute. }\hfill{(\textit{2019})}
	\item {Volunteered for an introductory session on \textbf{Python} which was conducted as a part of Bridge Course.}
	\hfill{(\textit{2019})}
    \item {Completed a \textbf{100 hrs} course on the \textbf{Chinese} language conducted by IR office, IIT Bombay. }\hfill{(\textit{2019})}
    \item {Completed a short term course on \textbf{Digital System Design} organised by \textbf{C-DAC,} Hyderabad.}\hfill{(\textit{2015})}
	\item {An active member of \textbf{National Service Scheme (NSS)} for 2 years and attended a camp conducted in a village to perform social activities like conducting medical camps, cleaning and painting common facilities like village panchayat, temple etc.} \hfill{(\textit{2013})}
     \item {Completed basic course in the \textbf{French} language from Vivekananda Institute of Languages, Hyderabad.}\hfill{(\textit{2012})}
   	\item {Volunteered for \textbf{$1^{st}$ World Parliament on Spirituality} for a week as part of NSS activity.}\hfill{(\textit{2012})}
    
    
\end{itemize}

%-------------------------------------------------------------------------------------------------



\end{document}
